\documentclass{article}
\usepackage{url}
\usepackage{hyperref}
\title{Using the IPRO Peer Review System\\For Students}
\author{Casey Bennett}

\begin{document}
\maketitle
\tableofcontents
\newpage

\section{Introduction}

The IPRO Peer Review System is an online application written in PHP that allows IPRO students to provide fellow students with feedback on their performance over the course of a semester.

\section{Getting Started}

Registration in the Peer Review System is done automatically sometime near the beginning of the semester. Your professor will let you know when he wishes Peer Review surveys to be completed.

To log into the Peer Review System, visit \url{http://sloth.iit.edu/~iproadmin/peerreview}. Your username and password are identical to those used for iGroups. If you are unabled to log in, you should first try resetting your password using the "Reset Password" link located under the login form. If resetting your password does not enable you to log in, contact \url{mailto:iproadmin@iit.edu}.

\section{Taking Surveys}

To begin a survey, click the "Take Survey" button corresponding to the person you wish to review.

A survey has two sections. The first section, Competency Rating, is a series of criteria which you can rank the person on, from 1 (not effective) to 5 (most effective). Complete each criterion. At the end of the Competency Rating section, you will be asked to rank the importance of your team member compared to the other members in your team, from 1 (most important) to n (least important), where n is the number of students in your team.

The second section is a written portion, where you can provide comments about this person. These comments will be provided to the person anonymously as part of his individual report after your team's Peer Review process is completed. This section is optional, but you are encouraged to provide constructive feedback here.

After you have completed the survey, double-check your responses. You may not go back and edit a survey once you have completed it, so ensure that the feedback you provided is accurate and adequate. When you are satisfied, click "Submit Survey".

You should repeat this procedure for every member of your team, including your own self-assessment.

\section{Viewing Surveys}

After you have completed a survey, you may not alter your responses, but you may still view them. For team members whose surveys you have completed, the button next to their names will be "View". Click this button to view the responses you gave.

You may also view a concise summary of all the surveys you have completed, by clicking on "All Reviews" on the left sidebar.

\section{Getting Help}

If you entered a score incorrectly and need to change it, please ask your instructor to email the IPRO Administrator. The IPRO office will not delete completed surveys without authorization from your instructor.

If you encounter a problem with the software, please email the IPRO Administrator at \url{mailto:iproadmin@iit.edu}.

\end{document}
